Lifting CDCL to Relational Domains

### 2016-10-13 conclusion.tex
conclusion
git update
effect of decision heuristics

\section{Conclusions}
In this paper, we instantiate ACDCL solver with different numerical domains -- 
intervals and octagons.  Experimental evaluation on different benchmarks shows that
ACDCL is able to suitably exploit the expressivity of richer
abstract domains as well as precision of CDCL architecture.
This is attributed to the intelligent decision heuristics
which exploits the high-level structure of the problem
combined with stronger deductions and clause learning
mechanism aided by the richer abstract domains.

>>>>

\section{Conclusions}
In this paper, we instantiate ACDCL solver with relational domains.  We explained specific properties of model search and conflict analysis procedure necessary
for such lifting.  Experimental evaluation on different benchmarks shows that
ACDCL is able to suitably exploit the expressivity of richer
abstract domains as well as precision of CDCL architecture.
This is attributed to the intelligent decision heuristics
which exploits the high-level structure of the problem
combined with stronger deductions and clause learning
mechanism aided by the richer abstract domains.

Future work -- domain refinement, incremental solving, invariant inference, intelligent $\gamma$-completeness check.

### 2016-10-13 experiments.tex
effect of decision heuristics

\section{Experimental Results}
We classify our benchmarks into two groups: {\em bounds checking}, 
{\em equivalence checking}.  We use interval, octagon, and equality 
domain for our verification task.  We analyze programs with bounded 
loops.  All loops in the program are completely unrolled before analysis.

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
in 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  To enable precise 
analysis using Astr{\'e}e, all our benchmarks are manually instrumented with 
partition directives which provides external hint to the tool to guide 
the trace partitioning heuristics.  Usually, such high-precision is not 
needed for static analysis, since it makes the analysis very expensive.  
Without trace partitioning, the analysis using Astr{\'e}e shows high 
degree of imprecision.

\paragraph {\em Observation of Analysis}

\paragraph {\em Decision Heuristics} We compare the performance of 
different decision heuristic on our benchmarks.  We observe that 
the ordered heuristic outperforms other heuristics on control-intensive 
benchmarks due to its ability to prioritize decisions on variables that 
appears in conditional branches.  For straight-line code and most of 
the bit-vector regression suite, random heuristics performs the best.  
Whereas, the activity based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for safe benchmarks 
that encountered maximum number of conflicts to prove safety.

\paragraph {\em Clause Learning}
